
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[letterspace=150]{microtype}
\usepackage{hyperref}

%font
\usepackage[familydefault,light]{Chivo} %% Option 'familydefault' only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\footskip = 5pt

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
%\newcommand{\resumeSubSubItem}[1]{}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
\begin{tabular}{c}
  \lsstyle
  {\Huge Group 7}\\ 
  Abdi Vicenciodelmoral $\bullet$ Benjamin Eavenson $\bullet$ Dwayne Butler \\
  Muniker Aragon $\bullet$ Pavel Roslyy $\bullet$ Trever Hibbs \\
\end{tabular}
\end{center}

%-----------PROJECTS-----------------
\section{\Large{\textbf{Projects}}}

% Example project entry
%===Title Of Project===%
  \resumeSubHeadingListStart
    \resumeSubheading{Title of Project}{technologies used}{short discription}
                     {start and end dates, i.e. August 2019 - August 2020}
    \resumeSubHeadingListStart
      \resumeSubItem{bold title of bullet1}{bullet 1}
      \resumeSubItem{bold title of bullet2}{bullet 2}
      \resumeSubItem{bold title of bullet3}{bullet 3}
    \resumeSubHeadingListEnd
  \resumeSubHeadingListEnd
  


%-----------EXPERIENCE-----------------
\section{\Large{\textbf{Relevant Experience}}}

  \resumeSubHeadingListStart
    \resumeSubheading
    {Computer Integration Club \href{http://www6.encs.vancouver.wsu.edu/}{\textit{(link)}}}{Washington State University}
    {}{August 2019 - Present}
      \resumeItemListStart
		\resumeItem{Full Stack Web Development}{Designed and implemented all front-end and back-end systems for club website.}
        \resumeItem{Website Hosting With Apache}{Setup Apache, Git, SQL, and created classes for communication between PHP, the database, and  front end template engine.}
        \resumeItem{Secure Login and Database}{Utilized encryption algorithms to generate password hashes and used back-end validation techniques to prevent SQL injection to keep self developed login system secure.}
        \resumeItem{Team Development}{Identified key features of site to create tasks for each member to coordinate development.}
      \resumeItemListEnd
      
    \resumeSubheading
    {CIMLS \href{https://www.cimls.com/}{\textit{(link)}}}{e1Solutions}
    {}{July 2017 - Present}
      \resumeItemListStart
   		\resumeItem{RESTful backend}{Developed class to integrate Census Bureau API for demographics system on site.}
        \resumeItem{Daily Cron Jobs}{Created cron scripts to maintain site and document site statistics.}
        \resumeItem{Google Recaptcha}{Developed class to integrate Google Recaptcha V3 into forms across the site to prevent bot access.}
        \resumeItem{Google SEO}{Implemented SEO best practices as outlined by Google, including maintaining canonical urls, using proper breadcrumbs, and modifying content to fit user need.}
        \resumeItem{Development of ccrealtygroup}{Setup git, database, and backend libraries to make code base modular and reusable.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd



%--------PROGRAMMING SKILLS------------
\section{\Large{\textbf{Programming Skills}}}

  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, C, PHP, HTML, CSS, JavaScript, MySQL}
      \hfill
      \textbf{Technologies}{: Linux, Git, Django, Bootstrap4, Smarty}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

